---
title: "Graph Overview"
author: "Joseph Kilgore"
date: "11/8/2019"
output:
  html_document: default
  pdf_document: default
---

## Source Files
Multiple files are loaded for this markdown document. Each has its own use, and were built with modularity, and meant to be taken apart, and tinkered with.

#### UsefulFunctions.R
This is a conglomeration of functions that are useful while analyzing data from the [Nerve-Block-Modeling Repository](https://github.com/joey-kilgore/Nerve-Block-Modeling/). Notably there are functions for loading entire sets of .csv files, and putting them into one dataframe.

#### 3DVoltage.R
Generates 3D voltage plots showing the voltage of multiple nodes over time.

#### VoltageProfile.R
Generate plot of all node voltage values at a given time.

#### defs.R
Keeps track of certain parameters (notably the dataset directory), which are used by multiple source files.

```{r setup, results='hide', warning=FALSE}
source("UsefulFunctions.R")
source("3DVoltage.R")
source("VoltageProfile.R")
source("defs.R")
```

## 3D Voltage Plots  
3D voltage plots allow showing voltage of multiple nodes over time. Unfortunately, 3d graphs are notorious for making some data hard to see.  
Regardless, they are a useful tool, and the following graph is an example of how they can show block. The following article is a reference to one of the earlier examples of this graphing technique.  

[Zhang, X., Roppolo, J., Groat, W. D., & Tai, C. (2005). Simulation Analysis of Nerve Block by High Frequency Biphasic Electrical Current Based on Frankenhaeuser-Huxley Model. 2005 IEEE Engineering in Medicine and Biology 27th Annual Conference. doi: 10.1109/iembs.2005.1615402](https://www.ncbi.nlm.nih.gov/pubmed/16200764)

```{r voltage3d, results='hide'}
voltagePlot3D()
```

## Voltage Profile Plots
Voltage profile plots give a method for observing the voltage of all nodes in a simulation. This is essentially a slice of the 3D voltage plot shown above, but showing all nodes instead of just a few. The following article is a reference to one of the earlier examples of this graphing technique.

[Bhadra, N., & Kilgore, K. (2004). Direct Current Electrical Conduction Block of Peripheral Nerve. IEEE Transactions on Neural Systems and Rehabilitation Engineering, 12(3), 313–324. doi: 10.1109/tnsre.2004.834205](https://www.ncbi.nlm.nih.gov/pubmed/15473193)

```{r voltageProfile, results='hide'}
voltageProfile()
```